---
title: "Plotly 3D Surface Data Visualization with Contour Lines"
author: "dB"
date: "`r Sys.Date()`"
output: ioslides_presentation
widescreen: true

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## Static Vehicle magnetic field measurements   

**Background:** Magnetometers can be used to measure changes in local magnetic fields caused by the influx of conductors. In this study, a matrix(15x7) of magnetometer sensor data were collected and analyzed. Seven magnetometers were aligned and placed on the pavement, to represent the x-axis, as the vehicle was driven over in 1ft increments, representing the y-axis.  

## **Experimental Setup:**

-  Seven magnetometer sensors aligned in a one-dimensional x-axis array equally spaced 2ft apart

-  2005 Audi TT Roadster convertible, curb weight 3,384 lbs, footprint dimensions 5'8” Width x 13'3” Length 

- Magnetometer readings (z=microgauss) were taken every 1ft (y-axis array) distance for a total matrix of (15x7) measurements

## **Results:**

- The highest peaks represent the engine and front-axle area occupying the highest concentration of metal conductors.    
- The driver is sitting at the wheel and his magnetic signature can easily be spotted.


##
```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
#install.packages("plotly")
# Install and load the R package mice
library(plotly)

#import data
#setwd(~Desktop)
#getwd()
file <- "Audi_Bz.csv"

data <- read.csv(file, header=FALSE, stringsAsFactors=FALSE)
#str(data)

data <- as.matrix(data, nrow = 15, ncol=13)
#data

plot_ly(z = data, type = "surface", colorscale="Picnic", contours = list(z = list(show = TRUE, start = 10, end = 250, size = 10)))
```
This graph is produced with Plotly 3-D Surface Plot and the commands are in upper right-hand corner of this graph. Hover over the upper right-hand corner of this graph and the interactive display commands with Plotly Logo will appear.

